|

### 2021-11-10 paper/dcpo_demsupport.Rmd
based on new data
address the comparison of SEM and MOC.

@@

<div id = 'refs_app'></div>

>>>>

A simultaneous equation model which incorporates measurement model and structural links between variables together accounts for bias caused by simultaneity between variables and measurement models.
However, we are reluctant to use a structural equation model (SEM) because SEM is a method to test the match between the model and the data.
In other words, SEM tests whether the assumed model can be validated by the observed data, with the assumption is that the model is correct.
Therefore, SEM is subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and  endogenous are contaminated by measurement errors [@Edith2019], among others [@Tomarken2005].

More importantly, SEM becomes more complicated by increasing equations, demanding more from researchers on specific projects, but our main idea is to demonstrate the importance of incorporating uncertainty in a broader context but also provide a practical technique for scholars to deal with a model with multiple latent variables in both sides of the model.

The advantage of MOC is that it can accommodate multiple layers of uncertainty in both opinion estimates and substantive models [@Kastellec2015, 792] and can be used very handily.

@@
